---
title: "NDVI Trace in Hayman Fire"
author: "Matthew Ross"
date: "9/5/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidyr)
library(ggthemes)
library(lubridate)
knitr::opts_chunk$set(echo = TRUE)
```

## Hayman Fire

In 2002 there was a large fire in central Colorado. This analysis is meant
to highlight how the fire altered vegetation in the area.


### Data read

First we have to read in the NDVI data which is structured to compare
unburned vs burned sites in the Hayman region. 

```{r data-read}
#Reading in the data. 
ndvi <- read_csv('data/hayman_ndvi.csv') %>%
  rename(burned=2,unburned=3) %>%
  filter(!is.na(burned),
         !is.na(unburned))


```

### Tidying 

Next we clean the data a little
```{r tidying}
# Converting from wide to long data
ndvi_long <- gather(ndvi,
                    key='site',
                    value='NDVI',
                    -DateTime)

```

### Plot of NDVI over time

NDVI (greenness) after the fire dramatically decreased and stayed low for at least
17 years. 
```{r plot-all}

# Plotting all the data
ggplot(ndvi_long,aes(x=DateTime,y=NDVI,color=site)) +
  geom_point(shape=1) +
  geom_line() +
  theme_few() + 
  scale_color_few() +
  theme(legend.position=c(0.3,0.3))


```

